---
title: "Matrix Norms"
output:
  pdf_document: default
  html_notebook: default
---
A "matrix norm" is a way of assigning a numerical measurement to a matrix. There are different types of matrix norms, each useful in their own context.

---

The _Frobenius norm_ is defined as follows:

#### $$||A||_{F} = \sqrt{\displaystyle \sum_{i = 1}^{n}\sum_{j=1}^{m}(A_{i,j})^2}$$

The function for the _Frobenius norm_ is written in R as follows:

```{r}
F.norm <- function(A) {
  sum_squares = 0
  for (i in 1:nrow(A)) {
    for (j in 1:ncol(A)) {
      sum_squares = sum_squares + A[i,j]^2
    }
  }
  return(sqrt(sum_squares))
}
```

The _1-norm_ is defined as follows:

#### $$||A||_{1} = \displaystyle \max_{1 \le j \le m}(\sum_{i=1}^{n}|A_{i,j}|)$$

The function for the _1-norm_ is written in R as follows:

```{r}
one.norm <- function(A) {
  n = nrow(A)
  m = ncol(A)
  col_sums = vector(length=m)
  for (j in 1:m) {
    sum = 0
    for (i in 1:n) {
      sum = sum + abs(A[i,j])
    }
    col_sums[j] = sum
  }
  return(max(col_sums))
}
```

The _$\infty$-norm_ is defined as follows:

#### $$||A||_{\infty} = \displaystyle \max_{1 \le i \le  n}(\sum_{j=1}^{n}|A_{i,j}|)$$

The function for the _$\infty$-norm_ is written in R as follows:

```{r}
inf.norm <- function(A) {
  n = nrow(A)
  m = ncol(A)
  row_sums = vector(length=n)
  for (i in 1:n) {
    sum = 0
    for (j in 1:m) {
      sum = sum + abs(A[i,j])
    }
    row_sums[i] = sum
  }
  return(max(row_sums))
}
```

---

The main Matrix Norm function is written in R as follows:

```{r}
mat.norm <- function(A, type=c("one", "inf", "F")) {
  switch (type,
    "one" = one.norm(A),
    "inf" = inf.norm(A),
    "F" = F.norm(A)
  )
}
```

---

 Homework 5 for MATH 366: _Applied Mathematical Computation_